---
title: "Reproducible Research project 1"
author: "MCH"
date: "Sunday, June 14, 2015"
output: html_document
---



read in the data and convert the dates to a date value

```{r, echo=TRUE} 
setwd("D:/Research/Data Science/Reproducible research/repdata_data_activity")
data = read.csv("activity.csv",header=T, colClass = c('integer','Date','integer'))

library(dplyr)
```


Calculate the total number of steps taken per day
```{r, echo=TRUE} 
steps_total <- data %>%
  filter(!is.na(steps))  %>%
  group_by(date)  %>%
  summarize(steps = sum(steps))  %>%
  print
```

Make a histogram of the total number of steps taken each day
```{r, echo=TRUE} 
barplot(steps_total$steps, xlab="Date", ylab = "Total steps per day",)
```


Calculate and report the mean and median of the total number of steps taken per day
```{r, echo=TRUE} 
mean_steps <-mean(steps_total$steps, na.rm = TRUE)
median_steps <- median(steps_total$steps, na.rm = TRUE)
```

Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis)
and the average number of steps taken, averaged across all days (y-axis)
```{r, echo=TRUE} 
five_interval <- data %>%
  filter(!is.na(steps)) %>%
  group_by(interval) %>%
  summarize(steps = mean(steps)) 
```

plot(five_interval, type ='l', ylab = "number of steps", main = ("Average steps by interval"))
  ```   

Which 5-minute interval, on average across all the days in the dataset, 
contains the maximum number of steps?
```{r, echo=TRUE} 
max_step_interval <- five_interval$interval[which.max(five_interval$steps)]
```
Calculate and report the total number of missing values in the dataset 
(i.e. the total number of rows with NAs)
```{r, echo=TRUE} 
missing_value <- sum(is.na(data$steps))
```


Sorry, ran out of time on this one. 

